---
title: "Summary of results for WNV mechanistic model"
author: "Morgan Kain and Ben Bolker"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

## This document provides a pdf summary of the results for each run of "top_level_script.R" 
### Primary results and aspects of the dataset are presented here. All other results have been saved to disk in "saved_output"

##### For *non-dynamic* (designed for our specific results) plots see: manuscript_figures.R. This script will produce some summaries, but not clean plots.

Note: This should be run using the rmarkdown::render( ) line in "top_level_script.R". "Knitting" it while the script is open in R studio for example will lead to errors (objects are not searched for in the global environment)


#### Dataset info


Number of communities in the "reduced data set" for the chosen number of complete lists: 

```{r number of communities, echo = FALSE}
nrow(effort_metadata_com %>% filter(num_lists >= 80))
```


Number of distinct bird species in the "reduced data set" for the chosen number of complete lists: 

```{r number of birds, echo = FALSE}
n_distinct(samp_data_com[["phylo_name"]])
```


#### R0 estimates


Median estimates among communities 

```{r R0 among communities, echo = FALSE}
ggplot(comm_comp_summary_p2, aes(med_comp)) + 
  geom_histogram(aes(y=..count..), bins = 100) + 
  geom_vline(xintercept = median(comm_comp_summary_p2[["med_comp"]])
    , linetype = "dotted", col = "grey", lwd = 1) +
    geom_vline(xintercept = median(comm_comp_summary_p2_well_observed[["med_comp"]])
    , linetype = "dotted", col = "blue", lwd = 1) +
  geom_histogram(data = comm_comp_summary_p2_well_observed, aes(y=..count..)
    , colour = "blue", bins = 100, fill = "blue") +
  geom_vline(xintercept = 1, linetype = "dashed", col = "black", lwd = 1) +
  geom_hline(yintercept = 0, colour = "white", size = 1) +
  xlab("Community R0") +
  ylab("Number of Communities")
```


Median width of the CI for R0 among communities 

```{r R0 CI width, echo = FALSE}
comm_comp_summary_p2_well_observed %>%
  summarize(median(max_comp - min_comp))
```


#### Spatio-temporal variation in R0

```{r spatio temporal, echo = FALSE}
summary(comm_comp_spatio_temporal_r[[2]])
```


#### Diluter and Amplifier species


Less of a refined plot than is presented in our text; just for a quick visual/summary.

```{r dilut amd amp species, echo = FALSE}
if (test_species_importance == TRUE) {

needed_packages <- c("extrafont", "scales", "tikzDevice")
if (length(setdiff(needed_packages, rownames(installed.packages()))) > 0) {
  install.packages(setdiff(needed_packages, rownames(installed.packages())))  
}

lapply(needed_packages, require, character.only = TRUE)
  
true_diluters_r_fp   <- true_diluters_r[true_diluters_r[["med_dilut_effect"]] > 1.01, ]
true_amplifiers_r_fp <- true_amplifiers_r[true_amplifiers_r[["med_dilut_effect"]] < 0.99, ]
  
species_importance_dat_for_plot <- rbind(true_diluters_r_fp, true_amplifiers_r_fp)
  
ggplot(species_importance_dat_for_plot
  , aes(med_dilut_effect, phylo_name, colour = n_com / max(n_com))) + 
  geom_errorbarh(aes(xmin = min_dilut_effect, xmax = max_dilut_effect), height = 0.2, lwd = 1) +
  geom_point(lwd = 3) + 
  geom_vline(xintercept = 1, linetype = "dashed", col = "black", lwd = 0.5) +
  xlab(expression(paste("Proportional Change in", italic(" R")[0], sep = " "))) +
  ylab("") +
  scale_colour_gradient2(low = muted("red"), mid = "grey", high = muted("blue"), midpoint = 0.50) +
  guides(color = guide_legend("Proportion of Communities")) + 
  theme(legend.key.size = unit(.55, "cm")
    , legend.position = c(0.2, 0.8)
    , axis.text.x = element_text(size = 12)
    , axis.text.y = element_text(size = 14)
    , axis.title.x = element_text(size = 12)
    , axis.title.y = element_text(size = 14))

} else {
  print("Species importance wasn't run")
}
```


Most common (widespread --- appears in the most lists) species

```{r common spec, echo = FALSE}
if (test_species_importance == TRUE) {
head(as.data.frame(species_importance_most_observed_r))
}  else {
  print("Species importance wasn't run")
}
```


Most abundant (raw counts) species

```{r abundant spec, echo = FALSE}
if (test_species_importance == TRUE) {
  head(as.data.frame(species_importance_most_abundant_r))
} else {
  print("Species importance wasn't run")
}
```


#### Dilution effect


Dilution effect assumption and prediction

```{r dilution effect spec, echo = FALSE}

if (no_uncer == TRUE) {

summary(dilut_eff_lm_red)

summary(dilut_eff_pred_lm_red)

} else {
  
summary(dilut_eff_lm_red)

summary(dilut_eff_pred_lm_red)

}

```

